%% start of file 'template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[letterpaper]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\usepackage{textcomp}
\usepackage{comment}
% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.85]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
    % Profile
    
\name{Artem Kulakevich}{}
\address{Beaverton, Oregon}
\phone[mobile]{503-750-3225}
\email{Artem3@pdx.edu}
\homepage{linkedin.com/in/artem-kulakevich/}
\begin{document}

    
\recipient{XXXXXX}{SOMECOMPANY, Inc.\\123 SOMESTREET\\CITY}
\date{\today}
\opening{To whom it may concern,}
\closing{Best Regards,}
%\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

\indent I am writing this 

I am going to be graduating from Portland State University this June with a Bachelor's degree in Electrical Engineering.  I have already started working on my Master's degree in Electrical Engineering with a focus on digital integrated circuits and embedded systems.  I am going to be halfway done with my MS degree by the end of this semester.  I have been working full time at Micro Systems Engineering for almost four years now, starting when I was barely 20 years old.   For work, I have done multiple official validations, verification, document updates, and have trained people on those document changes. 

I have done LabVIEW programming, Epson RC+ robot training, electrical motor wiring for multiple mains voltage robot controllers, and countless hours of troubleshooting electrical and mechanical failures.  I am also required to lead a small team of 8-9 specialists on production tasks a few days out of the week.

I am by far strongest with digital integrated circuits and embedded systems since most of my education has been focused on digital logic.  My programming skills are mostly self-taught but I did take classes on C++ and SystemVerilog.  I love software programming and working on embedded systems.
  
I look forward to speaking with you in further detail about the open \textbf{Silicon Validation Software Engineer} position at \textbf{Apple}.






\makeletterclosing

\end{document}